Manuscript Figures for Genome Biology

### 2018-05-01 manuscript_figures/manuscript_figures.Rmd
Updates to manuscript plotting
Reorder the axes in Figure 4, add submit a submit script, standardize file
locations relative to cwd, add upset plot (Figure 2E) as a panel in Figure
2, add option to only plot a subset of intersections in aggupset plotter.

```{r Figure2-load-data}
# Load packages and source benchmark FDR
library(data.table)
library(tidyr)
library(dplyr)
library(readr)
library(ggplot2)
library(magrittr)
library(cowplot)
library(purrr)
library(DESeq2)
library(tibble)
library(ggthemes)
library(R.utils)

## load helper functions
for (f in list.files("../R", "\\.(r|R)$", full.names = TRUE)) {
    source(f)
}

# set up data / results directories
resdir <- "yeast-results"
outdir <- "yeast-figs"
dir.create(outdir, showWarnings = FALSE)
```

@@

# maybe 2E? - doesn't return a ggplot object :( 
# fails to convert using ggplotify package
aggupset(de5, alpha=0.05, supplementary = FALSE, 
                       return_list = FALSE)

# Figure 2 (ALL)
Fig2 <- plot_grid(p1, p2, p3, p4, ncol = 2, 
          labels = LETTERS[1:4], label_size = 20)
Fig2 <- plot_grid(Fig2, leg, ncol = 2, rel_widths = c(1, 0.2))
#Fig2 <- plot_grid(Fig2, p5, ncol=1, rel_heights = c(1, 0.5),
#                 labels = c("", "E"), label_size = 20)
Fig2
ggsave(file.path(outdir, "Figure2.pdf"), width=10, height=8)
```

@@

## load helper functions
for (f in list.files("../R", "\\.(r|R)$", full.names = TRUE)) {
    source(f)
}

outdir <- "casestudy-figs"
dir.create(outdir, showWarnings = FALSE)

# assumes sb objects are in the following location, which contains subfolders
# for each casestudy (if this isn't true, then parsing the case study and 
# dataset names later on will be incorrect)
path <- "../../sb-objects/"
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
alpha <- 0.10

@@

# create tidy data frame where each row is a method / dataset observation
# of a rank 
ranks <- data.frame()
obj.names <- str_split(objects, pattern = "/")
casestudy <- unlist(lapply(obj.names, function(x) x[5] ))
dataset <- unlist(lapply(obj.names, function(x) x[6] ))

@@

  tmp <- estimatePerformanceMetrics(x, alpha, tidy=TRUE) %>%
    filter( performanceMetric == "rejections") %>%
    rename( method = blabel) %>%
    filter( is.na(param.alpha) | (param.alpha == alpha)) %>%
    filter( is.na(param.smooth.df) | (param.smooth.df == "3L")) %>%
    filter( !method == "unadjusted") %>%
    select( method, value ) %>%
    rename( nrejects = value) %>%
    mutate( method = gsub("-df03", "", method)) %>%
    mutate( method = gsub("-a10", "", method)) %>%
    na.omit() %>%
    mutate( rank = rank(nrejects) / n() ) %>%
    mutate(casestudy = casestudy[i],
           dataset = dataset[i])

  ranks <- rbind(ranks, tmp)
}

@@

>>>>

```{r Figure2-load-data}
# Load packages and source benchmark FDR
library(tidyr)
library(dplyr)
library(ggplot2)
library(magrittr)
library(cowplot)
library(tibble)
library(ggthemes)
library(grid)
library(SummarizedBenchmark)

## load helper functions
for (f in list.files("../datasets/R", "\\.(r|R)$", full.names = TRUE)) {
    source(f)
}

# assumes sb objects are in the following location, which contains subfolders
# for each casestudy (if this isn't true, then parsing the case study and 
# dataset names later on will be incorrect)
path <- "../sb-objects"

# set up results directorie
outdir <- "./figures"
dir.create(outdir, showWarnings = FALSE)

# point to where yeast results are (within 'path' defined above)
resdir <- file.path(path, "RNAseq/yeast-results")

# set alpha cutoff for plots that are fixed at a certain value of alpha
alpha <- 0.10
```

@@

# Figure 2E - upsetr plot -- this solution currently chops off left margin hist
aggupset(de5, alpha=alpha, supplementary = FALSE, 
                       return_list = FALSE, nintersects = 12)
grid.text("Mean overlap Over 100 Replications", x = 0.6, y = 0.97, 
          gp = gpar(fontsize = 16, fontface = "bold")) 
p5 <- grid.grab()

# Figure 2 (ALL)
Fig2 <- plot_grid(p1, p2, p3, p4, ncol = 2, 
          labels = LETTERS[1:4], label_size = 20)
Fig2 <- plot_grid(Fig2, leg, ncol = 2, rel_widths = c(1, 0.2))

Fig2 <- plot_grid(Fig2, p5, ncol=1, rel_heights = c(1, 0.5),
               labels = c("", "E"), label_size = 20)

Fig2
ggsave(file.path(outdir, "Figure2.pdf"), width=10, height=12)
```

@@

objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )

@@

# create tidy data frame where each row is a method / dataset observation
# of a rank 
ranks <- data.frame()
obj.names <- str_split(objects, pattern = "/")
casestudy <- unlist(lapply(obj.names, function(x) x[3] ))
dataset <- unlist(lapply(obj.names, function(x) x[4] ))

@@

  if (sum(hasResults) > 0){
    tmp <- estimatePerformanceMetrics(x, alpha, tidy=TRUE) %>%
      filter( performanceMetric == "rejections") %>%
      dplyr::rename( method = blabel) %>%
      filter( is.na(param.alpha) | (param.alpha == alpha)) %>%
      filter( is.na(param.smooth.df) | (param.smooth.df == "3L")) %>%
      filter( !method == "unadjusted") %>%
      select( method, value ) %>%
      dplyr::rename( nrejects = value) %>%
      mutate( method = gsub("-df03", "", method)) %>%
      mutate( method = gsub("-a10", "", method)) %>%
      na.omit() %>%
      mutate( rank = rank(nrejects) / n() ) %>%
      mutate(casestudy = casestudy[i],
             dataset = dataset[i])

    ranks <- rbind(ranks, tmp)
  }
}

@@

case_dat <- ranks_avg %>%
  group_by( casestudy) %>%
  summarize( nmethods = n())

method_dat <- ranks_avg %>%
  group_by( method) %>%
  summarize( meta_rank = mean(mean_rank))

ranks_avg <- left_join(ranks_avg, method_dat, by ="method")
ranks_avg <- left_join(ranks_avg, case_dat, by ="casestudy")

# reorder rows and columns
ranks_avg$casestudy <- factor(ranks_avg$casestudy, 
                              levels=unique(ranks_avg$casestudy[order(ranks_avg$nmethods)]))
ranks_avg$method <- factor(ranks_avg$method,
                           levels=unique(ranks_avg$method[order(ranks_avg$meta_rank)]))
